Solutions to Integer Programming from Quantum Annealing

### 2020-09-04 paper/main.tex
Brought simulation into intro

\begin{abstract}
 While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
 To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
 For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
 This work presents the formalism of how to map ILP problems to the annealing architectures.
 It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
 We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.

@@

>>>>

\begin{abstract}
 While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
 To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
 For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
 This work presents the formalism of how to map ILP problems to the annealing architectures.
 It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
 We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
 {\color{red}Furthermore we find evidence for Many-body localization effects ... and find that FC decoherence is more relevant than local decoherence...}

@@

To understand which quantum phenomena are relevant for describing the scaling behavior of the proposed offset study, we simulate the anneal for a small MDS problem.
This requires solving the von Neumann equations of the time dependent problem.
To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
 \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
\end{align}
where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
In this work, we consider two types of decoherence models: full counting statistics and local damping.
The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
The local damping term models the decoherence of each qubit independently.
